---
title: "WEEK 3 ASSIGNMENT"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

##makeCacheMatrix: This function creates a special "matrix" object that can cache its inverse##

```{r cars}
MakeCacheMatrix <- function(x = matrix()){
        i <- NULL
        set <- function(y){
                x<<- y
                i <<- NULL
        }
        get<-function() x
        setinverse<- function(inverse) i<<- inverse
        getinverse <- function() i 
        list(set = set, get = get, setinverse= setinverse, getinverse = getinverse)
}

```

## Including Plots

##cacheSolve: This function computes the inverse of the special "matrix" returned by makeCacheMatrix above. If the inverse has already been calculated (and the matrix has not changed), then the cachesolve should retrieve the inverse from the cache##

```{r pressure, echo=FALSE}
cacheSolve <- function(x, ...) {
        i <- x$getinverse()
        if(!is.null(i)) {
                message("getting cached data")
                return(i)
        }
        data <- x$get()
        i <- inverse(data, ...)
        x$setinverse(i)
        i
}
```

##Computing the inverse of a square matrix can be done with the solve function in R. For example, if X is a square invertible matrix, then solve(X) returns its inverse. For this assignment, assume that the matrix supplied is always invertible.##
```{r pressure, echo=FALSE}

```
